Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaEvolution.tex
Ongoing: Addressing Alexei's comments

The next LHC run for taking data (Run 3) will require more resources than the
Worldwide LHC Computing Grid (WLCG) can provide. Currently, PanDA WMS uses more
than 100,000 cores at over 100 Grid sites, with a peak performance of 0.3
petaFLOPS. This capacity will be sufficient for the planned analysis and data
processing, but it will be insufficient for the Monte Carlo production workflow
and any extra activity. To alleviate these challenges, ATLAS is engaged in a
program to expand the current computing model to include additional resources
such as the opportunistic use of supercomputers as well as commercial and
academic clouds.

@@

Detector simulation is part of the ATLAS production Monte Carlo (MC) workflow
(also known as MC production
chain)~\cite{rimoldi2006atlas,de2013delphes,ritsch2014atlas}. The MC workflow
consists of four main stages: event generation, detector simulation,
digitization, and reconstruction. Event generation creates sets of particle
four-momenta via different generators, e.g., PYTHIA~\cite{sjostrand2006pythia},
HERWIG~\cite{corcella2001herwig} and many others. The detector simulator is
called Geant4~\cite{agostinelli2003geant4} and simulates the interaction of
these particles with the sensitive material of the ATLAS detector. Each
interaction creates a so-called hit and all hits are collected and passed on for
digitalization where hits are further process to mimic the readout of the
detector. Finally, reconstruction operates local pattern recognition, creating
high-level objects like particles and jets.

>>>>

The next LHC run for taking data (Run 3) will require more resources than the
Worldwide LHC Computing Grid (WLCG) can provide. Currently, PanDA WMS uses more
than
% 100,000
300,000 cores at over 100 Grid sites\mtnote{Addresses Alexei's comment.
Increased Grid capacity to 300K cores. Is the number of sites still 100 or
should I increase that too?}, with a peak performance of 0.3 petaFLOPS. This
capacity will be sufficient for the planned analysis and data processing, but it
will be insufficient for the Monte Carlo production workflow and any extra
activity. To alleviate these challenges, ATLAS is engaged in a program to expand
the current computing model to include additional resources such as the
opportunistic use of supercomputers as well as commercial and academic clouds.

@@

Detector simulation is part of the ATLAS production Monte Carlo (MC) workflow
(also known as MC production
chain)~\cite{rimoldi2006atlas,de2013delphes,ritsch2014atlas}. The MC workflow
consists of four main stages: event generation, detector simulation,
digitization, and reconstruction. Event generation creates sets of particle
four-momenta via different generators, e.g., PYTHIA~\cite{sjostrand2006pythia},
HERWIG~\cite{corcella2001herwig} and many others. \mtnote{Addresses Alexei's comment. Is the following sentence correct?} The detector simulator is
called Geant4~\cite{agostinelli2003geant4} and simulates both the ATLAS detector and it's interaction physical processes.
% the interaction of these particles with the sensitive material of the ATLAS
% detector.
Each interaction creates a so-called hit and all hits are collected and passed
on for digitalization where hits are further process to mimic the readout of the
detector. Finally, reconstruction operates local pattern recognition, creating
high-level objects like particles and jets.
